### 2016-05-04 p01-ch02-2013/paper.tex
Fix a cascaded paraph spacing issue

\parbf{How to send a message with a deadline?} 
% Let us consider that object $o$ sends message $m$ to object $o'$ with deadline $d$:
The construct
$$
f = e_0 \; ! \; m(\overline{e}) \; \textbf{\jtt{deadline}}(e_1)
$$
describes an asynchronous message with a deadline specified by $e_1$ (of type $\mathsf{T}_{time}$).
Deadlines  can be specified  using a notion of time unit such as millisecond, second, minute or other units of time.
% The value of the deadline $d$ is relative from the perspective of the caller object $o$.
% The value of the deadline $d$ is translated in the side of callee object $o'$ to an absolute value in a transparent way.
The caller expects the  callee (denoted by $e_0$) to process   the message  within the  units of time
specified by $e_1$.
Here processing a message means starting the execution of the process generated by the message.
A deadline  is missed if and only if the callee  does not  start  processing  the message within the specified units of time.
% In other words, deadline $d$ is missed if the response for message $m$ is not ready within $d$ unit of time at the side of object $o'$.
% \textsl{Note} that we do not consider I/O, infrastructure, and network times as part of the effective times of processing message $m$ 
% and sending the correspondent response.

\parbf{What happens when a deadline is missed?}
Messages received by an actor generate processes.
Each actor contains one active process and all its other processes are queued. 
Newly generated processes are \emph{inserted} in the queue according to an application-specific policy.
When a \emph{queued} process misses its deadline it is \emph{removed} from the queue and a
corresponding \emph{exception} is recorded by its future (as described below).
When the currently active process is terminated the process at the head of the queue is activated
(and as such  dequeued).
The active process  cannot be \emph{preempted} and is forced
to  \emph{run to completion}.
In  Section \ref{ch02:sec:impl} we discuss the implementation details of this design choice.

\parbf{How to process the response of a message with a deadline?}
In the above example of an asynchronous message, the \emph{future} result of processing the  message   
is denoted by the  variable $f$ which has the type of \textbf{\jtt{Future}}.
Given a future variable $f$, the programmer can query  the  availability of the  result by the construct

$$
v = f.\gett(e)
$$
The execution of the \gett \space operation terminates successfully when  the future variable $f$ contains the result value.
In case the future variable $f$ records an exception, e.g. in case the corresponding process has missed its  deadline,
the \gett\space operation is \emph{aborted} and the exception is \emph{propagated}. 
Exceptions can be caught by \jtt{try-catch} blocks.

@@

In the local  transition system we make use of the following axiomatization of the occurrence of exceptions.
Here $(S,\sigma,\phi)\uparrow v$ indicates that $S$  raises an exception $v$:
\begin{itemize}\itemsep5pt
 \item $ (x=f.\gett(),\sigma,\phi) \uparrow \sigma(f)$ where $\phi(\sigma(f)).\mathsf{aborted}=\jtt{true}$,
 \item $\frac{\displaystyle (S,\sigma,\phi)\uparrow v}{\trycatch{S}{T}{u}{S'}\uparrow v}$ where $v$ is not of type $\mathsf{T}$, and, 
 \item $\frac{\displaystyle (S,\sigma,\phi)\uparrow v}{\displaystyle (S;S,\sigma,\phi) '\uparrow v}$.
\end{itemize}

@@

\parbf{Assignment statement} is used to assign a value to a variable:

@@

\parbf{Returning a result} consists of setting the field 
\textsf{val} of the future of the process:

@@

\parbf{Initialization of \jtt{timeout} in \gett  \space operation} 
assigns to a  distinguished (local) variable \jtt{timeout} its initial \emph{absolute} value:
\begin{multline*} \langle  (x=f.\gett(e); S, \sigma), q, \phi\rangle \rightarrow  \\
 \langle (x=f.\gett(e);S, \sigma [\jtt{timeout} \mapsto \textsf{val}(e+\mathsf{time})(\sigma), q, \phi\rangle 
\end{multline*}

\parbf{The \gett \space operation} is used to assign the value of a future to a variable:
$$ \langle  (x=f.\gett(); S, \sigma), q, \phi\rangle \rightarrow \langle (S, \sigma [x \mapsto \phi(\sigma(f)).\mathsf{val}]), q, \phi\rangle $$
where $ \phi(\sigma(f)).\mathsf{val} \neq \bot$ .

\parbf{Timeout} is operationally presented by the following transition:
$$ \langle  (x=f.\gett(); S, \sigma), q, \phi\rangle \rightarrow \langle (S, \sigma), q, \phi\rangle $$
where $\sigma(\jtt{time})< \sigma(\jtt{timeout})$.

\parbf{The \textnormal{\textbf{\jtt{try-catch}}} block} semantics is presented by:

@@

\parbf{Exception handling.} 
We provide the operational semantics of exception handling in a general way in the following:
$$
\frac
{(S,\sigma,\phi) \uparrow v}
{\langle (\trycatch{S}{T}{x}{S''};S''', \sigma), q, \phi\rangle \rightarrow \langle  (S'';S''', \sigma[x\mapsto v]), q, \phi\rangle}
$$
where the exception $v$ is  of type \jtt{T}.

\parbf{Abnormal termination} of the active process is generated by an uncaught exception:
$$
\frac
{(S,\sigma,\phi)\uparrow v}
{\langle (S;S', \sigma), q, \phi\rangle \rightarrow \langle (S'',\sigma'), q', \phi'\rangle}
$$
where $q = (S'',\tau) \cdot q' $ and $\sigma'$ is obtained from restoring the values of the local variables
as specified by $\tau$ (formally, $\sigma'(x)=\sigma(x)$, for every instance variable $x$, and $\sigma'(x)=\tau(x)$, for every local variable $x$), and  $\phi'(\sigma(\jtt{myfuture})).\jtt{aborted} = \jtt{true}$
($\phi'(o)=\phi(o)$, for every $o\not= \sigma(\jtt{myfuture})$).

\parbf{Normal termination} is presented by:
$$
\langle (E, \sigma), q, \phi\rangle \rightarrow \langle  (S,\sigma'), q', \phi\rangle
$$
where $q = (S,\tau) \cdot q'$ and $\sigma'$ is obtained from restoring the values of the local variables
as specified by $\tau$ (see above).
We denote by $E$ termination (identifying $S;E$ with $S$).

\parbf{Deadline missed.}
Let  $(S', \tau)$ be some  pending process  in $q$ such that $\tau(\textbf{\jtt{deadline}}) < \sigma(\jtt{time})$.
Then
$$
\langle  (S,\sigma), q, \phi\rangle \rightarrow \langle p, q', \phi'\rangle 
$$
where $q'$ results from $q$ by removing $(S',\tau)$ and $\phi'(\tau(\jtt{myfuture})).\jtt{aborted} = \jtt{true}$
($\phi'(o)=\phi(o)$, for every $o\not= \tau(\jtt{myfuture})$).

@@

\parbf{Incoming message.}
Let the active process $p$ belong to the actor $\tau(\jtt{this})$ (i.e., 
 $\sigma(\jtt{this})=\tau(\jtt{this})$ for the assignment $\sigma$ in $p$):
$$
\langle p , q, \phi\rangle \xrightarrow[]{m(\tau)}  \langle p , \mathsf{insert}(q, m(\overline{v}, d)), \phi\rangle
$$
where   $\mathsf{insert}(q, m(\tau))$  defines the result of inserting the process  $(S,\tau)$, where $S$ denotes the body of method $m$,
in $q$, according to some application-specific policy (described below in Section \ref{ch02:sec:impl}).

\parbf{Outgoing message.} 
We model an outgoing message by:
$$
\langle (f = e_0 \; ! \; m(\bar{e}) \; \textbf{\jtt{deadline}}(e_1);S,\sigma)  , q, \phi\rangle 
\xrightarrow[]{m(\tau)} 
\langle (S,\sigma[f\mapsto o])  , q, \phi' \rangle 
$$
where 
\begin{itemize}\itemsep5pt
\item $\phi'$ results from $\phi$ by extending its domain  with a new future object $o$
such that $\phi'(o).\textsf{val}=\perp$\footnote{$\perp$ stands for "uninitialized"}and $\phi'(o).\textsf{aborted}=\jtt{false}$,
 \item $\tau(\jtt{this})=\textsf{val}(e_0)(\sigma)$,
 \item $\tau(x)= \textsf{val}(e)(\sigma)$, for every formal parameter $x$ and corresponding actual parameter $e$, 
 \item $\tau(\jtt{deadline})=\sigma(\mathsf{time})+ \textsf{val}(e_1)(\sigma)$,
  \item  $\tau(\jtt{myfuture})=o$.
\end{itemize}

@@

\parbf{Local computation step.} 
The interleaving of local computation steps of the individual actors is
modeled by the rule:
$$
\frac{(s, \phi) \rightarrow (s', \phi')}
{(\{s\}\cup\Sigma, \phi)\rightarrow (\{s'\}\cup\Sigma, \phi')}
$$

\parbf{Communication.} 
Matching a  message sent by one actor with its  reception by  the specified callee
is described by the rule:
$$
\frac
{(s_1, \phi) \xrightarrow[]{m(\tau)} (s'_1, \phi')\quad (s_2, \phi) \xrightarrow[]{m(\tau)} (s'_2, \phi) }
{(\{s_1,s_2\}\cup\Sigma, \phi) \rightarrow (\{s'_1 , s'_2 \} \cup \Sigma, \phi')}
$$
Note that only an outgoing message affects the shared heap $\phi$ of futures.

\parbf{Progress of Time.}
The following transition uniformly updates the local clocks (represented by the instance variable \jtt{time})
of the actors.
$$
(\Sigma,\phi)\rightarrow (\Sigma',\phi)
$$
where
$$
\Sigma'=\{\langle (S,\sigma'), q, \phi\rangle\mid
\langle (S,\sigma), q, \phi\rangle\in \Sigma,\; \sigma'=\sigma [\jtt{time}\mapsto \sigma(\jtt{time})+\delta]\}
$$
for some positive $\delta$.

@@

\parbf{Deploying actors onto JVM threads.}
%As a major improvement to our previous work \cite{crisp-sac}, we changed the model of deployment of actors onto Java threads for simplicity, performance, and better reasoning.
In the implementation, each actor owns a main thread of execution, that is,
the implementation does \emph{not} allocate \emph{one} thread per process because
threads are  \emph{costly} resources and
allocating to each process one thread in general leads to a poor performance:
there can be an arbitrary number of actors in the application and each may receive numerous messages which thus give rise to  a number of threads that  goes beyond the  limits of memory and resources.
Additionally, when processes go into pending mode, their correspondent thread may be reused for other processes.
Thus, for better performance and optimization of resource utilization, the implementation assigns a single thread for all processes inside each actor.

@@

%\parbf{Implementation of $(S, \tau)$ and $(S, \sigma)$.} 
%As discussed, when an actor receives an incoming message, a process is created for the messages.
%Within the process creation, the process allocates a data structure that behaves as a repository for the process.
%When the process is pending, the process has only access to the local variables and actual parameters of the message.
%When the process is executing, the access is extended to the level of actor's instance variables.
%The access level is managed by Crisp's core architecture when transferring the process from pending state to executing state (and the other way).
%At either state, the process has access to special convenient instances/methods including \jtt{myActor}, \jtt{myFuture}, \jtt{myDeadline};
%respectively, they denote the owning actor for the process, the future that will be the result of the process, and the deadline specified for the process.

\parbf{Implementation of processes with deadlines.}
A process itself is represented in the implementation by a data structure
which encapsulates the values of its local variables and the method to be executed.
Given a relative deadline $d$ as specified by a call
we compute at run-time its absolute deadline (i.e. the expected starting time of the process) by
$$
 \jtt{TimeUnit.toMillis}(d) + \jtt{System.currentTimeMillis()}
$$
which is a \emph{soft} real-time requirement.
%As shown in the above equation, the received deadline is expected to express a \emph{relative} amount of time.
%Each actor maintains a queue of processes to be executed along with the reference to the current executing process.
As in the operational semantics, in the real-time implementation
always the head of the process queue  is scheduled for execution.
This allows the implementation of a \emph{default}
earliest deadline first (EDF) scheduling policy
by  maintaining a queue ordered by  the above absolute time values for the deadlines.

@@

\parbf{Fredhopper case study.}
As introduced in Section \ref{ch02:sec:frh}, we extract a closed-world simplified version from Fredhopper Controller.
We apply the approach discussed in this paper to use deadlines for asynchronous messages.
% Controller operates in a high-demand distributed setting as in Figure \ref{ch02:fig:ctl:deploy}.

>>>>

\paragraph*{How to send a message with a deadline?} 
% Let us consider that object $o$ sends message $m$ to object $o'$ with deadline $d$:
The construct
$$
f = e_0 \; ! \; m(\overline{e}) \; \textbf{\jtt{deadline}}(e_1)
$$
describes an asynchronous message with a deadline specified by $e_1$ (of type $\mathsf{T}_{time}$).
Deadlines  can be specified  using a notion of time unit such as millisecond, second, minute or other units of time.
% The value of the deadline $d$ is relative from the perspective of the caller object $o$.
% The value of the deadline $d$ is translated in the side of callee object $o'$ to an absolute value in a transparent way.
The caller expects the  callee (denoted by $e_0$) to process   the message  within the  units of time
specified by $e_1$.
Here processing a message means starting the execution of the process generated by the message.
A deadline  is missed if and only if the callee  does not  start  processing  the message within the specified units of time.
% In other words, deadline $d$ is missed if the response for message $m$ is not ready within $d$ unit of time at the side of object $o'$.
% \textsl{Note} that we do not consider I/O, infrastructure, and network times as part of the effective times of processing message $m$ 
% and sending the correspondent response.

\paragraph*{What happens when a deadline is missed?}
Messages received by an actor generate processes.
Each actor contains one active process and all its other processes are queued. 
Newly generated processes are \emph{inserted} in the queue according to an application-specific policy.
When a \emph{queued} process misses its deadline it is \emph{removed} from the queue and a
corresponding \emph{exception} is recorded by its future (as described below).
When the currently active process is terminated the process at the head of the queue is activated
(and as such  dequeued).
The active process  cannot be \emph{preempted} and is forced
to  \emph{run to completion}.
In  Section \ref{ch02:sec:impl} we discuss the implementation details of this design choice.

\paragraph*{How to process the response of a message with a deadline?}
In the above example of an asynchronous message, the \emph{future} result of processing the  message   
is denoted by the  variable $f$ which has the type of \textbf{\jtt{Future}}.
Given a future variable $f$, the programmer can query  the  availability of the  result by the construct
$$
v = f.\gett(e)
$$
The execution of the \gett \space operation terminates successfully when  the future variable $f$ contains the result value.
In case the future variable $f$ records an exception, e.g. in case the corresponding process has missed its  deadline,
the \gett\space operation is \emph{aborted} and the exception is \emph{propagated}. 
Exceptions can be caught by \jtt{try-catch} blocks.

@@

In the local  transition system we make use of the following axiomatization of the occurrence of exceptions.
Here $(S,\sigma,\phi)\uparrow v$ indicates that $S$  raises an exception $v$:
\begin{itemize}
 \item $ (x=f.\gett(),\sigma,\phi) \uparrow \sigma(f)$ where $\phi(\sigma(f)).\mathsf{aborted}=\jtt{true}$,
 \item $\frac{\displaystyle (S,\sigma,\phi)\uparrow v}{\trycatch{S}{T}{u}{S'}\uparrow v}$ where $v$ is not of type $\mathsf{T}$, and, 
 \item $\frac{\displaystyle (S,\sigma,\phi)\uparrow v}{\displaystyle (S;S,\sigma,\phi) '\uparrow v}$.
\end{itemize}

@@

\paragraph*{Assignment statement} is used to assign a value to a variable:

@@

\paragraph*{Returning a result} consists of setting the field 
\textsf{val} of the future of the process:

@@

\paragraph*{Initialization of \jtt{timeout} in \gett  \space operation} 
assigns to a  distinguished (local) variable \jtt{timeout} its initial \emph{absolute} value:
\begin{multline*} \langle  (x=f.\gett(e); S, \sigma), q, \phi\rangle \rightarrow  \\
 \langle (x=f.\gett(e);S, \sigma [\jtt{timeout} \mapsto \textsf{val}(e+\mathsf{time})(\sigma), q, \phi\rangle 
\end{multline*}

\paragraph*{The \gett \space operation} is used to assign the value of a future to a variable:
$$ \langle  (x=f.\gett(); S, \sigma), q, \phi\rangle \rightarrow \langle (S, \sigma [x \mapsto \phi(\sigma(f)).\mathsf{val}]), q, \phi\rangle $$
where $ \phi(\sigma(f)).\mathsf{val} \neq \bot$ .

\paragraph*{Timeout} is operationally presented by the following transition:
$$ \langle  (x=f.\gett(); S, \sigma), q, \phi\rangle \rightarrow \langle (S, \sigma), q, \phi\rangle $$
where $\sigma(\jtt{time})< \sigma(\jtt{timeout})$.

\paragraph*{The \textnormal{\textbf{\jtt{try-catch}}} block} semantics is presented by:

@@

\paragraph*{Exception handling.} 
We provide the operational semantics of exception handling in a general way in the following:
$$
\frac
{(S,\sigma,\phi) \uparrow v}
{\langle (\trycatch{S}{T}{x}{S''};S''', \sigma), q, \phi\rangle \rightarrow \langle  (S'';S''', \sigma[x\mapsto v]), q, \phi\rangle}
$$
where the exception $v$ is  of type \jtt{T}.

\paragraph*{Abnormal termination} of the active process is generated by an uncaught exception:
$$
\frac
{(S,\sigma,\phi)\uparrow v}
{\langle (S;S', \sigma), q, \phi\rangle \rightarrow \langle (S'',\sigma'), q', \phi'\rangle}
$$
where $q = (S'',\tau) \cdot q' $ and $\sigma'$ is obtained from restoring the values of the local variables
as specified by $\tau$ (formally, $\sigma'(x)=\sigma(x)$, for every instance variable $x$, and $\sigma'(x)=\tau(x)$, for every local variable $x$), and  $\phi'(\sigma(\jtt{myfuture})).\jtt{aborted} = \jtt{true}$
($\phi'(o)=\phi(o)$, for every $o\not= \sigma(\jtt{myfuture})$).

\paragraph*{Normal termination} is presented by:
$$
\langle (E, \sigma), q, \phi\rangle \rightarrow \langle  (S,\sigma'), q', \phi\rangle
$$
where $q = (S,\tau) \cdot q'$ and $\sigma'$ is obtained from restoring the values of the local variables
as specified by $\tau$ (see above).
We denote by $E$ termination (identifying $S;E$ with $S$).

\paragraph*{Deadline missed.}
Let  $(S', \tau)$ be some  pending process  in $q$ such that $\tau(\textbf{\jtt{deadline}}) < \sigma(\jtt{time})$.
Then
$$
\langle  (S,\sigma), q, \phi\rangle \rightarrow \langle p, q', \phi'\rangle 
$$
where $q'$ results from $q$ by removing $(S',\tau)$ and $\phi'(\tau(\jtt{myfuture})).\jtt{aborted} = \jtt{true}$
($\phi'(o)=\phi(o)$, for every $o\not= \tau(\jtt{myfuture})$).

@@

\paragraph*{Incoming message.}
Let the active process $p$ belong to the actor $\tau(\jtt{this})$ (i.e., 
 $\sigma(\jtt{this})=\tau(\jtt{this})$ for the assignment $\sigma$ in $p$):
$$
\langle p , q, \phi\rangle \xrightarrow[]{m(\tau)}  \langle p , \mathsf{insert}(q, m(\overline{v}, d)), \phi\rangle
$$
where   $\mathsf{insert}(q, m(\tau))$  defines the result of inserting the process  $(S,\tau)$, where $S$ denotes the body of method $m$,
in $q$, according to some application-specific policy (described below in Section \ref{ch02:sec:impl}).

\paragraph*{Outgoing message.} 
We model an outgoing message by:
$$
\langle (f = e_0 \; ! \; m(\bar{e}) \; \textbf{\jtt{deadline}}(e_1);S,\sigma)  , q, \phi\rangle 
\xrightarrow[]{m(\tau)} 
\langle (S,\sigma[f\mapsto o])  , q, \phi' \rangle 
$$
where 
\begin{itemize}
\item $\phi'$ results from $\phi$ by extending its domain  with a new future object $o$
such that $\phi'(o).\textsf{val}=\perp$\footnote{$\perp$ stands for "uninitialized"}and $\phi'(o).\textsf{aborted}=\jtt{false}$,
 \item $\tau(\jtt{this})=\textsf{val}(e_0)(\sigma)$,
 \item $\tau(x)= \textsf{val}(e)(\sigma)$, for every formal parameter $x$ and corresponding actual parameter $e$, 
 \item $\tau(\jtt{deadline})=\sigma(\mathsf{time})+ \textsf{val}(e_1)(\sigma)$,
  \item  $\tau(\jtt{myfuture})=o$.
\end{itemize}

@@

\paragraph*{Local computation step.} 
The interleaving of local computation steps of the individual actors is
modeled by the rule:
$$
\frac{(s, \phi) \rightarrow (s', \phi')}
{(\{s\}\cup\Sigma, \phi)\rightarrow (\{s'\}\cup\Sigma, \phi')}
$$

\paragraph*{Communication.} 
Matching a  message sent by one actor with its  reception by  the specified callee
is described by the rule:
$$
\frac
{(s_1, \phi) \xrightarrow[]{m(\tau)} (s'_1, \phi')\quad (s_2, \phi) \xrightarrow[]{m(\tau)} (s'_2, \phi) }
{(\{s_1,s_2\}\cup\Sigma, \phi) \rightarrow (\{s'_1 , s'_2 \} \cup \Sigma, \phi')}
$$
Note that only an outgoing message affects the shared heap $\phi$ of futures.

\paragraph*{Progress of Time.}
The following transition uniformly updates the local clocks (represented by the instance variable \jtt{time})
of the actors.
$$
(\Sigma,\phi)\rightarrow (\Sigma',\phi)
$$
where
$$
\Sigma'=\{\langle (S,\sigma'), q, \phi\rangle\mid
\langle (S,\sigma), q, \phi\rangle\in \Sigma,\; \sigma'=\sigma [\jtt{time}\mapsto \sigma(\jtt{time})+\delta]\}
$$
for some positive $\delta$.

@@

\paragraph*{Deploying actors onto JVM threads.}
%As a major improvement to our previous work \cite{crisp-sac}, we changed the model of deployment of actors onto Java threads for simplicity, performance, and better reasoning.
In the implementation, each actor owns a main thread of execution, that is,
the implementation does \emph{not} allocate \emph{one} thread per process because
threads are  \emph{costly} resources and
allocating to each process one thread in general leads to a poor performance:
there can be an arbitrary number of actors in the application and each may receive numerous messages which thus give rise to  a number of threads that  goes beyond the  limits of memory and resources.
Additionally, when processes go into pending mode, their correspondent thread may be reused for other processes.
Thus, for better performance and optimization of resource utilization, the implementation assigns a single thread for all processes inside each actor.

@@

%\paragraph*{Implementation of $(S, \tau)$ and $(S, \sigma)$.} 
%As discussed, when an actor receives an incoming message, a process is created for the messages.
%Within the process creation, the process allocates a data structure that behaves as a repository for the process.
%When the process is pending, the process has only access to the local variables and actual parameters of the message.
%When the process is executing, the access is extended to the level of actor's instance variables.
%The access level is managed by Crisp's core architecture when transferring the process from pending state to executing state (and the other way).
%At either state, the process has access to special convenient instances/methods including \jtt{myActor}, \jtt{myFuture}, \jtt{myDeadline};
%respectively, they denote the owning actor for the process, the future that will be the result of the process, and the deadline specified for the process.

\paragraph*{Implementation of processes with deadlines.}
A process itself is represented in the implementation by a data structure
which encapsulates the values of its local variables and the method to be executed.
Given a relative deadline $d$ as specified by a call
we compute at run-time its absolute deadline (i.e. the expected starting time of the process) by
$$
 \jtt{TimeUnit.toMillis}(d) + \jtt{System.currentTimeMillis()}
$$
which is a \emph{soft} real-time requirement.
%As shown in the above equation, the received deadline is expected to express a \emph{relative} amount of time.
%Each actor maintains a queue of processes to be executed along with the reference to the current executing process.
As in the operational semantics, in the real-time implementation
always the head of the process queue  is scheduled for execution.
This allows the implementation of a \emph{default}
earliest deadline first (EDF) scheduling policy
by  maintaining a queue ordered by  the above absolute time values for the deadlines.

@@

\paragraph*{Fredhopper case study.}
As introduced in Section \ref{ch02:sec:frh}, we extract a closed-world simplified version from Fredhopper Controller.
We apply the approach discussed in this paper to use deadlines for asynchronous messages.
% Controller operates in a high-demand distributed setting as in Figure \ref{ch02:fig:ctl:deploy}.
